\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://hypex.co.uk/}{\seticon{faLink} hYPEX}} $|$ \emph{Xcart, PHP, MySQL, Vue.js, LazySizes, jQuery UI, jQuery, Bootstrap, etc.,  etc.}}{BERI}
\resumeItemListStart
\resumeItem{Maintained the hypex website using CSS,JS and Template Modification, focusing on responsive design, and consistent UI/UX.}
\resumeItem{Managed and updated detailed product listings, optimizing content with SEO strategies to enhance visibility and search engine rankings.}
\resumeItem{Collaborated cross-functionally to improve website performance, resulting in faster load times and increased user engagement.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{\href{https://www.beri.com.bd/}{\seticon{faLink} Beri}} $|$ \emph{Wordpress, PhP, MySQL, Apache,  etc.}}{Beri}
\resumeItemListStart
\resumeItem{Bangladesh Education and Research Institute (BERI) is a center of education and research excellence supported by advanced knowledge of information technology. It brings affordable, high-quality education opportunities to Bangladesh and is a leading offshore enterprise product and software development initiative.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{\href{https://orbit-middle-east.vercel.app/home}{\seticon{faLink} Orbit Middle East}} $|$ \emph{React, Git, Docker, Java Spring Boot, MySQL, AWS,  etc.}}{BERI}
\resumeItemListStart
\resumeItem{Anintegrated platform for Manage Multiple organizations and evaluate KPI Factors like Measure, Perspective,Objective, and Initiative.}
\resumeItem{This platform is designed to streamline operations, enhance productivity, and provide valuable insights for organizations in the Middle East.}
\resumeItem{Based on that some Visualization like briefing, chart, report, dashboard and strategy map Generated.}
\resumeItem{Onreport section Structure Data Report, Annual Data Report, By Calendar Data Report, Scorecard Attributes Data Report, etc.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{\href{https://taskroto.isubroto.com.bd}{\seticon{faLink} Taskroto}} $|$ \emph{Git, Next.js, PostgreSQL, Docker, Express.js, Node.js,  etc.}}{Own}
\resumeItemListStart
\resumeItem{These tools help individuals and teams organize, prioritize, and track tasks to ensure timely completion. They often include features like task lists, progress tracking, collaboration tools, and deadline management.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{\href{https://skythr.isubroto.com.bd/}{\seticon{faLink} Skythr}} $|$ \emph{Git, React, PostgreSQL, Docker,  etc.}}{Own}
\resumeItemListStart
\resumeItem{This weather application likely provides users with up-to-date meteorological information for various locations. It would typically offer details such as current temperature, humidity, wind speed, precipitation chances, and forecasts for the coming hours or days.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{\href{https://potrfolio.isubroto.com.bd/}{\seticon{faLink} Subroto Saha Portfolio}} $|$ \emph{Git, React, PostgreSQL, Docker,  etc.}}{Own}
\resumeItemListStart
\resumeItem{This portfolio website showcases the work and skills of Subroto Saha, a software engineer. It likely includes information about his projects, experience, and contact details, serving as a digital resume and professional showcase.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{AI CHATBOT} $|$ \emph{Git, Linux, Docker, Python, AWS, VueJs, Jira, etc.,  etc.}}{Own}
\resumeItemListStart
\resumeItem{A chat bot Made with Python that is based on natural language can interact with humans to replay some trained questions.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{RASAJS} $|$ \emph{Git, Linux, Docker, Express.js, Node.js, etc.,  etc.}}{Own}
\resumeItemListStart
\resumeItem{The Rasa Node.js API enables integration of Rasa chatbots or voice assistants into Node.js applications via HTTP requests, allowing you to send messages, receive responses, and track conversation history.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{RASALOG} $|$ \emph{Git, Linux, Docker, Express.js, Node.js, mongoDB, etc.,  etc.}}{Own}
\resumeItemListStart
\resumeItem{A log system for Rasa chat records captures and stores details of user interactions with the Rasa chatbot, including message texts, timestamps, user or session IDs, and relevant contextual information.}
\resumeItemListEnd
\resumeSubHeadingListEnd
